Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Add missing TBD
Minor clarification
Add a hint for vim to set textwidth to 70
Adapt Hspec examples
Use Specs instead of Spec, and hspec instead of hspecX.

%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------

@@

%%%% Describe the problem.
\begin{quote}
    Important points we want to say:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            BDD approaches \emph{Test-driven development (TDD)} and
            \emph{Acceptance test-driven development (ATDD)} with a new
            terminology and mindset .  For the purpose of this paper we focus
            on the TDD aspect of BDD.
        \item
            Automating things, and continuous integration is an important
            aspect of BDD.
    \end{itemize}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
import Test.Hspec.Monadic
spec :: Specs
spec = do
  describe "reverse" $ do
    it "reverses a list" $
      reverse [1 :: Int, 2, 3] @?= [3, 2, 1]

@@

A spec can be run with the \texttt{hspecX} function.  When a spec is run, all
properties and examples are evaluated, and failing properties and examples are
reported to the user (FIXME: user does not fit our definition of \emph{user}
here!).

@@

main :: IO ()
main = hspecX $ do
  describe "Foo"     FooSpec.spec
  describe "Foo.Bar" Foo.BarSpec.spec
  describe "Baz"     BazSpec.spec
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
-- file Spec.hs
import Test.Hspec.Monadic
main = hspecX spec
\end{verbatim}
\end{quote}

>>>>

% vim: tw=70
%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------

@@

\begin{quote}
\emph{NOTE: @sol has to release a new version of hspec, that includes
the Spec-to-Specs and hspecX-to-hspec changes.  Otherwise the code in
this paper will not work!}
\end{quote}

%%%% Describe the problem.
\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            BDD approaches \emph{Test-driven development (TDD)} and
            \emph{Acceptance test-driven development (ATDD)} with a new
            terminology and mindset .  For the purpose of this paper we focus
            on the TDD aspect of BDD.
        \item
            Automating things, and continuous integration is an important
            aspect of BDD.
    \end{itemize}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
import Test.Hspec.Monadic
spec :: Spec
spec = do
  describe "reverse" $ do
    it "reverses a list" $
      reverse [1 :: Int, 2, 3] @?= [3, 2, 1]

@@

A spec can be run with the \texttt{hspec} function.  When a spec is run, all
properties and examples are evaluated, and failing properties and examples are
reported to the user (FIXME: user does not fit our definition of \emph{user}
here!).

@@

main :: IO ()
main = hspec $ do
  describe "Foo"     FooSpec.spec
  describe "Foo.Bar" Foo.BarSpec.spec
  describe "Baz"     BazSpec.spec
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
-- file Spec.hs
import Test.Hspec.Monadic
main = hspec spec
\end{verbatim}
\end{quote}
